### 2018-03-30 metrics.tex
did some cleanng heare and there
som edits before submission
First draft of revision.

These metrics are listed in Table \ref{tab:metrics}. Following \citet{Anderson_2004_Proc}, when applied to a pair of signals, each one of these metrics yields a GOF score ranging from 0 to 10, where a value of 10 corresponds to two signals having identical characteristics. This scoring scale varies according to the following exponential function:
% 
\begin{equation}
\label{eq:gof-function}
	S \left( p_1, p_2 \right) = 10 \exp{ \left[ - \left( \frac{p_1 - p_2}{ \min\left( p_1, p_2 \right) } \right)^2 \right] }
	\, ,
\end{equation}
% 
\noindent
where $S$ is the GOF score that results from comparing values $p_1$ and $p_2$ from signals 1 and 2, respectively, for each one of the different metrics in Table \ref{tab:metrics}. \citeauthor{Anderson_2004_Proc} also provided guidelines for the process to be applied to the original signals as well as to those resulting from a sequential set of band-pass filters covering the whole frequency range of interest. In his method, this frequency-domain decomposition should have pass bands defined following a logarithmic distribution in order to give more weight to the low-frequencies, and the GOF scores of all sub-bands and the broadband be averaged into a single GOF final score.

@@

\citet{Anderson_2004_Proc} calibrated the results of GOF scores comparing horizontal components of recorded seismograms and other simulations using the first ten metrics (C1 through C10) in Table \ref{tab:metrics}. He concluded that for a typical distribution of the scores, the GOF could be categorized into four groups: poor (for scores from 0 to 4), fair (4 to 6), good (6 to 8), and excellent (for scores from 8 to 10). While this categorization was arguably subjective, over the years it has become common practice and has been adopted or matched by alternative validation methods \citep[e.g.,][]{Kristekova_2009_GJI, Olsen_2010_SRL}, making the method itself a reference baseline for various validation studies \citep[e.g.,][]{Chaljub_2010_BSSA, Bielak_2010_GJI, Guidotti_2011_SRL, Maufroy_2015_BSSA}.

@@

% ===========================================================================================
%
% OLD NAEEM VERSION
% 
% Following the guidelines suggested by \citet{Anderson_2004_Proc}, \citet{Taborda_2014_BSSA} applied the scoring procedure to each pair of data and synthetic using compatible broadband sets, and series of bandpass filtered versions of the signals or sub-bands, SB1, SB2, SB3, SB4, and SB5. The signals bandpass filtered between 0.1 and 4 Hz for BB, and between 0.1 Hz and 0.25 Hz, and 0.25 and 0.5 Hz, and 0.5 and 1 Hz, and 1 and 2 Hz, and 2 and 4 Hz for SB1, SB2, SB3, SB4, and SB5, respectively. They also reported a scaled combination score of metrics and bands. However, since the combined scores are linear scaled combinations of metrics and frequency bands, in this specific study, they do not add new information to the data base.  \citet{Khoshnevis_2015_Proc} studied the effect of filtering on GOF score and presented that filtering approach can affect the GOF score and change the final classes. Therefore, in order to avoid extra source of uncertainty in the study, we only consider broadband GOF scores ($0.1-4~Hz$). Analysis of effect of bands in the results could be an appropriate subject for another study.

% Accuracy of ground motion simulation is evaluated based on a quantitative validation of the simulation ground motions. The validation process consist of comparisons between synthetics and data, at locations where records were available for the simulated events. For validating the simulation of strong motion complex time series, different metrics are defined. These metrics evaluate the similarity of two signals in time or frequency domain. \\

% \citet{Anderson_2004_Proc} proposed 10 individual quality measures to evaluate the credibility of synthetic seismograms.  He proposed to apply the metrics on 10 frequency bands with logarithmic spacing. The logarithmic spacing puts more emphasis on lower frequencies where these frequencies are more amenable to waveform fitting and are particularly important for response of large structures. A comprehensive score (S1) could be achieved by the average of the scores of seismograms filtered in each of the valid frequency bands individually, as well as the broadband seismogram. An alternative score (S2) is obtained by averaging the scores on the ten individual criteria for only the accelerogram filtered to allow all frequencies to pass. \citet{Anderson_2004_Proc} scaled the scores into range of 0 to 10 with 10 giving perfect agreement. He suggested to consider a score below 4 as a poor fit, a score of 4-6 as a fair fit, a score of 6 to 8 as a good fit, and a score over 8 is an excellent fit. However, some of these metrics like integral measures are potentially very easy to fit and some of them like cross correlation is by far the most difficult of all parameters to achieve high score. Therefore, for a pair of synthetic and data some of metrics could belong to good and some of them could belong to fair fit classes.\\

% In other study, \citet{Kristekova_2006_BSSA} developed quantitative misfit criteria for comparison of seismograms. The misfit criteria are defined based on the time-frequency (TF) representation of the seismograms obtained at the continues wavelet transform. Based on local TF envelop and phase differences, they defined envelop and phase misfit dependent on both time and frequency. With projection of TF misfit onto frequency or time domain, they computed frequency- or time-dependent misfits, respectively. The method proposed  by \citet{Kristekova_2006_BSSA} needs to consider one of signals as a reference signal. Therefore, \citet{Kristekova_2009_GJI} presented an extension of the theory of the TF misfit criteria. They defined locally and globally normalized TF criteria where locally normalized misfits can be used if it is important to investigate relatively small part of the signal. The globally normalized misfits can be used for quantifying an overall level of disagreement. In the extended version of the metrics, they defined a misfit criteria for 3 components of a signal and also they developed TF GOF criteria for more realistic scenario where there is a high level of disagreement and it is not possible to consider one of signals as a reference signal. They classified the GOF scores as poor, fair, good, and excellent based on GOF numerical values.\\

% \citet{Olsen_2010_SRL} argued that the \citet{Kristekova_2006_BSSA,Kristekova_2009_GJI}  metrics are suitable for low frequency signals. Therefor, they proposed a new GOF method for validation of Broadband synthetics. They used some of metrics that are used by \citet{Anderson_2004_Proc}, however, they used different scoring approach which generates a relatively high-resolution representation of small misfits. They also used inelastic and elastic response spectra ration (IE ratio) as a structural engineering specific metric. They proposed to combine the metrics for final decisions based on user defined application-based weights.\\

% Recently, \citet{Taborda_2013_BSSA} conducted a simulation for 2008 Chino Hills earthquake and proposed a minor modification in the \citet{Anderson_2004_Proc} metrics. They added an eleventh parameter to the Anderson's scores as strong motion duration.\\

% A comprehensive validation approach should include metrics in both time and frequency domain. All mentioned metrics \citep[i.e.,][]{Anderson_2004_Proc,Kristekova_2006_BSSA,Kristekova_2009_GJI,Olsen_2010_SRL} have this characteristic. However, in this study we are mostly dependent on available data based on \citet{Taborda_2014_BSSA} where they used the GOF method proposed by \citet{Anderson_2004_Proc}, with minor modification introduced by \citet{Taborda_2013_BSSA}. The method compares synthetics against data using 11 individual parameters, namely: Arias Intensity Integral (C1), Energy Integral (C2), Arias Intensity Value (C3), Total Energy (C4), Peak Acceleration (C5), Peak Velocity (C6), Peak Displacement (C7), Response Spectra (C8), Fourier Amplitude Spectrum (C9), Cross Correlation (C10), and Strong Phase Duration (C11). Each parameter is mapped on to a numerical scale ranging from 0 to 10, where a score of 10 corresponds to a perfect  match between two signals.\\
% Following the guidelines suggested by \citet{Anderson_2004_Proc}, \citet{Taborda_2014_BSSA} applied the scoring procedure to each pair of data and synthetic using compatible broadband sets, and series of bandpass filtered versions of the signals or sub-bands, SB1, SB2, SB3, SB4, and SB5. The signals bandpass filtered between 0.1 and 4 Hz for BB, and between 0.1 Hz and 0.25 Hz, and 0.25 and 0.5 Hz, and 0.5 and 1 Hz, and 1 and 2 Hz, and 2 and 4 Hz for SB1, SB2, SB3, SB4, and SB5, respectively. They also reported a scaled combination score of metrics and bands. However, since the combined scores are linear scaled combinations of metrics and frequency bands, in this specific study, they do not add new information to the data base.  \citet{Khoshnevis_2015_Proc} studied the effect of filtering on GOF score and presented that filtering approach can affect the GOF score and change the final classes. Therefore, in order to avoid extra source of uncertainty in the study, we only consider broadband GOF scores ($0.1-4~Hz$). Analysis of effect of bands in the results could be an appropriate subject for another study.

>>>>

These metrics are listed in Table \ref{tab:metrics}. Following \citet{Anderson_2004_Proc}, when applied to a pair of signals, each one of these metrics yields a GOF score ranging from 0 to 10, where a value of 10 corresponds to two signals having identical characteristics. This scoring scale varies according to the following exponential function
% 
\begin{equation}
\label{eq:gof-function}
	S \left( p_1, p_2 \right) = 10 \exp{ \left[ - \left( \frac{p_1 - p_2}{ \min\left( p_1, p_2 \right) } \right)^2 \right] }
	\, ,
\end{equation}
% 
\noindent
where $S$ is the GOF score that results from comparing values $p_1$ and $p_2$ from signals 1 and 2, respectively, for each one of the different metrics in Table \ref{tab:metrics}. \citeauthor{Anderson_2004_Proc} also provided guidelines for the process to be applied to the original signals as well as to those resulting from a sequential set of band-pass filters covering the whole frequency range of interest. In his method, this frequency-domain decomposition should have pass bands defined following a logarithmic distribution in order to give more weight to the low-frequencies, and the GOF scores of all sub-bands and the broadband be averaged into a single GOF final score. \myrevision{However, in this study, in order to reduce the uncertainties that can come from different filtering process \citep[e.g., see ][]{Khoshnevis_2015_Proc} we use broadband results (\feq{0}{4}). For metrics which are functions of frequency (or period) like Fourier spectra and response spectra, the final result is the mean value of application of equation(\ref{eq:gof-function}) on all frequencies (or periods).}

@@

\citet{Anderson_2004_Proc} calibrated the results of GOF scores comparing horizontal components of recorded seismograms and other simulations using the first ten metrics (C1 through C10) in Table \ref{tab:metrics}. He concluded that for a typical distribution of the scores, the GOF could be categorized into four groups: poor (for scores from 0 to 4), fair (4 to 6), good (6 to 8), and excellent (for scores from 8 to 10). While this categorization was arguably subjective, over the years it has  \myrevision{ been frequently used and} \myremove{become common practice and has} been adopted or matched by alternative validation methods \citep[e.g.,][]{Kristekova_2009_GJI, Olsen_2010_SRL}, making the method itself a reference baseline for various validation studies \citep[e.g.,][]{Chaljub_2010_BSSA, Bielak_2010_GJI, Guidotti_2011_SRL, Maufroy_2015_BSSA}.

@@

### 2018-03-30 results.tex
First draft of revision.

\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-06}
	\caption{Statistical distribution of the dataset as partitioned into the four validation categories (poor, fair, good, excellent) after the clustering analysis. The distributions are shown in the form of box-plots for each metric (C1 through C11). In each case, the median is indicated by a notch in the box of the central quartiles, and the lines represent the interquartile range, with outliers shown as scattered dots. The color version of this figure is available only in the electronic edition.}
	\label{fig:boxed-clusters}
\end{figure*}

In total, the clustering process results in 816, 1253, 879 and 76 data samples for the poor, fair, good and excellent classes, respectively. These groups are shown in Fig.~\ref{fig:count-classes}. As it can be seen in this figure, the number of samples in the excellent class is significantly less than those in the poor, fair, and good classes. Therefore, before moving on with the decision tree analysis, it is necessary to resample the subset of the excellent class. We used the oversampling approach described in the previous section. We replicated data from the excellent class randomly by a $\times$10 factor until elevating the number of samples in this class to 760 as indicated in Fig.~\ref{fig:count-classes} with the dashed line. By common standards, an oversample rate of $\times$10 is considered acceptable \citep{Weiss_2003_JAIR}. (Arguably, we could have as well undersampled the fair class, but we deemed that unnecessary. Instead, we used a strong pruning process to prevent overfitting.) Once this process was completed we went on with the decision tree analysis.

@@

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-08}
	\caption{Accuracy of tree predictions in terms of the factor ($F_1$) from equation \ref{eq:f} as indicated by colored dots distributed with respect to the number of attributes (GOF metrics) as a function of: \textbf{(a)} the number of nodes, and \textbf{(b)} the depth of the trees. The rings around some of the dots indicate select trees used as reference in the text, other figures and tables. The color version of this figure is available only in the electronic edition.}
	\label{fig:nodes-depth}
\end{figure*}

@@

Based on these criteria, we selected three candidate trees: T1, T2, and T3. These trees are shown in Fig.~\ref{fig:trees}. T1 is the simplest of the three, and T2 and T3 share some of their topology on the right-hand side. T3 is the most complex of them. More complex trees tend to be deeper, have more nodes, and employ more attributes. This leads to higher $F_1$ values, but they may not necessarily be more practical. In total T1, T2, and T3 use 2, 3 and 4 attributes respectively. All coincide in the use of the total energy (C4) and response spectra (C8) as key metrics. T2 adds peak acceleration (C5), and T3 adds peak velocity (C5) to the previous metrics.

@@

At the bottom of each tree in Fig.~\ref{fig:trees} are the histograms of the data that land on each leaf node. (Note that the count of samples here is done based on the training dataset.) The decision tree assigns the final validation category based on the dominant class in each leaf. As such, the samples in the second leaf-node from the right in T3 are categorized as good despite a significant portion of them being excellent. This is a natural trade-off embedded in the use of decision trees which actually results in more effective trees.

@@

Notice that in all trees the metrics C4 (total energy) and C8 (response spectra) are consistently the most relevant ones in the decision algorithms. They are followed by C5 (peak acceleration) and C6 (peak velocity). On the other end, notice that C11 (strong phase duration) plays no role whatsoever in any of the trees, and that C1 (Arias integral), C2 (energy integral), and C3 (Arias intensity) have only small to marginal participations. The remaining metrics---C7 (peak displacement), C9 (Fourier spectrum), and C10 (Cross correlation)---have a somewhat significant participation, but only in the more complex trees.

A low participation does not necessarily mean that a given metric is not important. Arguably, the strong phase duration is highly regarded as an important parameter for strong motion records in engineering. What the results we present here mean, in the context of GOF validation, is that in order to classify whether a simulation result is poor, fair, good, or excellent, other metrics such as energy (C8) are much more decisive in reaching an accurate conclusion about validation quality than the duration (C11).

@@

\begin{table}[t]
	\centering
	\caption{Metrics data analysis participation in select trees (in percent)}
	\label{tab:participation}
	\small
	\begin{tabular}{lrrrr}
	Metric 	& T1 	& T2	& T3 	& T66 	\\ 
	\hline
	C1 		& --	& --	& -- 	& 1.5	\\
	C2 		& -- 	& --	& -- 	& 0.5	\\
	C3 		& -- 	& -- 	& -- 	& 9.6	\\
	\rowcolor{light-light-gray}
	C4 		& 46.8	& 52.4	& 60.2	& 100.0	\\
	\rowcolor{light-light-gray}
	C5 		& -- 	& 21.5	& 21.5	& 72.2	\\
	\rowcolor{light-light-gray}
	C6 		& -- 	& -- 	& 37.0	& 56.3	\\
	C7 		& -- 	& -- 	& -- 	& 19.4	\\
	\rowcolor{light-light-gray}
	C8 		& 100.0	& 100.0	& 100.0	& 100.0	\\
	C9 		& -- 	& -- 	& --	& 23.8	\\
	C10		& -- 	& -- 	& -- 	& 22.2	\\
	C11		& -- 	& -- 	& -- 	& -- 	\\
	\hline
	\end{tabular}
\end{table}

>>>>

\begin{figure*}
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-06_mod}
	\caption{Statistical distribution of the dataset as partitioned into the four validation categories (poor, fair, good, excellent) after the clustering analysis. The distributions are shown in the form of box-plots for each metric (C1 through C11). In each case, the median is indicated by a notch in the box of the central quartiles, and the lines represent the interquartile range, with outliers shown as scattered dots. The color version of this figure is available only in the electronic edition. \myrevision{Dashed lines represent the boundaries of poor, fair, good, and excellent categories according to  \citeauthor{Anderson_2004_Proc}'s method.}}
	\label{fig:boxed-clusters}
\end{figure*}

In total, the clustering process results in 816, 1253, 879 and 76 data samples for the poor, fair, good and excellent classes, respectively. These groups are shown in Fig.~\ref{fig:count-classes}. As it can be seen in this figure, the number of samples in the excellent class is significantly less than those in the poor, fair, and good classes. Therefore, before moving on with the decision tree analysis, it is necessary to resample the subset of the excellent class. We used the oversampling approach described in the previous section. We replicated data from the excellent class \myrevision{through random selection of data from that class until elevating the number of samples in this class to 760 as indicated in Fig.~\ref{fig:count-classes} with the dashed line. This oversampling is considered as a $\times$10 factor.} \myremove{randomly by a $\times$10 factor until elevating the number of samples in this class to 760 as indicated in Fig.~\ref{fig:count-classes} with the dashed line.} By common standards, an oversample rate of $\times$10 is considered acceptable \citep{Weiss_2003_JAIR}. (Arguably, we could have as well undersampled the fair class, but we deemed that unnecessary. Instead, we used a \myremove{strong} \myrevision{heavy} pruning process to prevent overfitting.) Once this process was completed we went on with the decision tree analysis.

@@

%\begin{figure*}[t]
%	\centering
%	\includegraphics[width=\textwidth]{figures/pdf/figure-08}
%	\caption{Accuracy of tree predictions in terms of the factor ($F_1$) from equation \ref{eq:f} as indicated by colored dots distributed with respect to the number of attributes (GOF metrics) as a function of: \textbf{(a)} the number of nodes, and \textbf{(b)} the depth of the trees. The rings around some of the dots indicate select trees used as reference in the text, other figures and tables. The color version of this figure is available only in the electronic edition.}
%	\label{fig:nodes-depth}
%\end{figure*}

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-08_mod}
	\caption{Accuracy of tree predictions in terms of the factor ($F_1$) from equation \ref{eq:f} as indicated by colored dots distributed with respect to the number of attributes (GOF metrics) as a function of: \textbf{(a)} the number of nodes, and \textbf{(b)} the depth of the trees. The rings around some of the dots indicate select trees used as reference in the text, other figures and tables. The color version of this figure is available only in the electronic edition.}
	\label{fig:nodes-depth}
\end{figure*}

@@

Based on these criteria, we selected three candidate trees: T1, T2, and T3. These trees are shown in Fig.~\ref{fig:trees}. T1 is the simplest of the three, and T2 and T3 share some of their topology on the right-hand side. T3 is the most complex of them. More complex trees tend to be deeper, have more nodes, and employ more attributes. \myrevision{complexity of trees is controlled by pruning process.} This leads to higher $F_1$ values, but they may not necessarily be more practical. In total T1, T2, and T3 use 2, 3 and 4 attributes respectively. All coincide in the use of the total energy (C4) and response spectra (C8) as key metrics. T2 adds peak acceleration (C5), and T3 adds peak velocity \myremove{(C5)} \myrevision{(C6)} to the previous metrics.

@@

At the bottom of each tree in Fig.~\ref{fig:trees} are the histograms of the data that land on each leaf node. (Note that the count of samples here is done based on the training dataset.) The decision tree assigns the final validation category based on the dominant class in each leaf. As such, the samples in the second leaf-node from the right in T3 are categorized as good despite a significant portion of them being excellent. This is a natural trade-off embedded in the use of \myrevision{pruned} decision trees which actually results in more effective trees.

@@

Notice that in all trees \myrevision{,using all metrics,} the metrics C4 (total energy) and C8 (response spectra) are consistently the most relevant ones in the decision algorithms. They are followed by C5 (peak acceleration) and C6 (peak velocity). On the other end, notice that C11 (strong phase duration) plays no role whatsoever in any of the trees, and that C1 (Arias integral), C2 (energy integral), and C3 (Arias intensity) have only small to marginal participations. The remaining metrics---C7 (peak displacement), C9 (Fourier spectrum), and C10 (Cross correlation)---have a somewhat significant participation, but only in the more complex trees.

\myrevision{It is obvious that C8(response spectra) and C5(peak acceleration) are the most important metrics in developing the prediction models. Therefore, in order to understand other parameters importance we developed two sets of trees according to complexity of the original trees (the structure of generated trees are not presented here), while once dropping C8 (response spectra) and once dropping C8 (response spectra) and C5(peak acceleration) from the prediction attributes. According to Table \ref{tab:participation}, these trees also emphasize the importance of C4 and C6. However, in the absence of C5(peak acceleration) and C8 (response spectra),  C3 (Arias intensity) and C9 (Fourier spectrum) become more effective in developing prediction models. Also C11(strong phase duration) becomes somewhat important in the most complicated tree.}

A low participation does not necessarily mean that a given metric is not important. Arguably, the strong phase duration is highly regarded as an important parameter for strong motion records in engineering. What the results we present here mean, in the context of GOF validation \myrevision{for engineering applications} , is that in order to classify whether a simulation result is poor, fair, good, or excellent, other metrics such as energy (C8) are much more decisive in \myrevision{narrowing eleven validation metrics into fewer numbers in order to get the same categorization as all eleven metrics}  \myremove{reaching an accurate conclusion about validation quality} than the duration (C11).

@@

%\begin{table}[t]
%	\centering
%	\caption{Metrics data analysis participation in select trees (in percent)}
%	\label{tab:participation}
%	\small
%	\begin{tabular}{lrrrr}
%	Metric 	& T1 	& T2	& T3 	& T66 	\\ 
%	\hline
%	C1 		& --	& --	& -- 	& 1.5	\\
%	C2 		& -- 	& --	& -- 	& 0.5	\\
%	C3 		& -- 	& -- 	& -- 	& 9.6	\\
%	\rowcolor{light-light-gray}
%	C4 		& 46.8	& 52.4	& 60.2	& 100.0	\\
%	\rowcolor{light-light-gray}
%	C5 		& -- 	& 21.5	& 21.5	& 72.2	\\
%	\rowcolor{light-light-gray}
%	C6 		& -- 	& -- 	& 37.0	& 56.3	\\
%	C7 		& -- 	& -- 	& -- 	& 19.4	\\
%	\rowcolor{light-light-gray}
%	C8 		& 100.0	& 100.0	& 100.0	& 100.0	\\
%	C9 		& -- 	& -- 	& --	& 23.8	\\
%	C10		& -- 	& -- 	& -- 	& 22.2	\\
%	C11		& -- 	& -- 	& -- 	& -- 	\\
%	\hline
%	\end{tabular}
%\end{table}

\begin{table}[t]
	\centering
	\caption{Metrics data analysis participation in select trees (in percent). \myrevision{Stars represent the trees with same complexity in pruning process, however, not exact tree structures.}}
	\label{tab:participation}
	\small
	\myrevision{
	\begin{tabular}{lrrrrrrrrrrrr}
	Metric 	& T1 	& T2	& T3 	& T66  & T1* 	& T2*	& T3* 	& T66*  & T1* 	& T2*	& T3* 	& T66* 	\\ 
	\hline
	&\multicolumn{4}{c}{Including C8} & \multicolumn{4}{c}{Without C8}&  \multicolumn{4}{c}{Without C5 and C8}\\
	\hline
	C1 		& --	& --	& -- 	& 1.5 & --	& --	& -- 	& --- & --	& --	& -- 	& --	\\
	C2 		& -- 	& --	& -- 	& 0.5 & --	& --	& -- 	& 2.27 & --	& --	& -- 	& --	\\
	C3 		& -- 	& -- 	& -- 	& 9.6 & --	& --	& -- 	& 53.22 & --	& 60.35	& 61.19 	& 99.11	\\
	\rowcolor{light-light-gray}
	C4 		& 46.8	& 52.4	& 60.2	& 100.0  & 44.35	& 81.77	& 81.77 	& 83.20 & 47.44	& 48.67	& 80.54 	& 54.64	\\
	\rowcolor{light-light-gray}
	C5 		& -- 	& 21.5	& 21.5	& 72.2 & 100.0	& 100.0	& 100.0 	& 100.0 & --	& --	& -- 	& --	\\
	\rowcolor{light-light-gray}
	C6 		& -- 	& -- 	& 37.0	& 56.3 & 58.65	& 63.51	& 62.77 	& 82.39 & 100.0	& 100	& 100 	& 100\\
	C7 		& -- 	& -- 	& -- 	& 19.4 & --	& --	& -- 	& 32.37 & --	& --	& -- 	& 43.24	\\
	\rowcolor{light-light-gray}
	C8 		& 100.0	& 100.0	& 100.0	& 100.0 & --	& --	& -- 	& --	 & --	& --	& -- 	& --\\
	C9 		& -- 	& -- 	& --	& 23.8 & --	& --	& -- 	& 48.63 & --	& --	& -- 	& 72.22	\\
	C10		& -- 	& -- 	& -- 	& 22.2 & --	& --	& -- 	& 24.93 & --	& --	& -- 	& 20.46	\\
	C11		& -- 	& -- 	& -- 	& -- 	    & --	& --	& -- 	& --- & --	& --	& -- 	& 8.09\\
	\hline
	\end{tabular}
	}
\end{table}

### 2018-03-30 testing.tex
First draft of revision.

In our view, the T1 results are simpler to assimilate and equally informative. Looking at both plots in Fig.~\ref{fig:avg-gof-maps} it is possible to argue they lead to the same conclusions and present a similar picture of the validation of the simulation, not only globally but at specific locations, with only minor differences---especially if one is to consider the assumed equivalence between scores and classes (0--4: poor; 4--6: fair; 6--8:good; 8--10: excellent).

@@

>>>>

In our view, the T1 results are simpler to assimilate and equally informative. Looking at both plots in Fig.~\ref{fig:avg-gof-maps} it is possible to argue they lead to \myremove{the same} \myrevision{similar} conclusions and present a similar picture of the validation of the simulation, not only globally but at specific locations, with only minor differences---especially if one is to consider the assumed equivalence between scores and classes (0--4: poor; 4--6: fair; 6--8:good; 8--10: excellent). \myrevision{However, we do not expect to see the same results in both figures. \citet{Taborda_2014_BSSA} results is developed based on assigning uniform weight on all metrics, however, this study research question is addressing the importance of different metrics and implying that assigning uniform weights might not provide accurate results.}

@@

\myrevision{It is worth mentioning that, in this study, we presented an integration of scientists knowledge and field data using machine learning algorithms to develop an acceptable and robust prediction model. This method can be used in any field where there are some field data as well as expertise knowledge about the data. Validation metrics are note limited to \citeauthor{Anderson_2004_Proc}'s metrics. Therefore, adding more metrics from different field can be used through the proposed method to develop prediction models. }
